RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2014-01-09 papers/rjournal/eddelbuettel-stokely.Rnw
Comment out an unneeded section now obviated by Jereoen's OpenCPU section.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@725 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Application: Distributed Data Collection with MapReduce}

TODO(mstokely): Make this better.

Many large data sets in fields such as particle physics and
information processing are stored in binned or histogram form in order
to reduce the data storage requirements
\citep{scott2009multivariate}. Protocol Buffers make a particularly
good data transport format in distributed MapReduces environments
where large numbers of computers process a large data set for analysis.

There are two common patterns for generating histograms of large data
sets with MapReduce.  In the first method, each mapper task can
generate a histogram over a subset of the data that is has been
assigned, and then the histograms of each mapper are sent to one or
more reducer tasks to merge.

In the second method, each mapper rounds a data point to a bucket
width and outputs that bucket as a key and '1' as a value.  Reducers
then sum up all of the values with the same key and output to a data store.

In both methods, the mapper tasks must choose identical
bucket boundaries even though they are analyzing disjoint parts of the
input set that may cover different ranges, or we must implement
multiple phases.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{histogram-mapreduce-diag1.pdf}
\end{center}
\caption{Diagram of MapReduce Histogram Generation Pattern}
\label{fig:mr-histogram-pattern1}
\end{figure}

Figure~\ref{fig:mr-histogram-pattern1} illustrates the second method
described above for histogram generation of large data sets with
MapReduce.

This package is designed to be helpful if some of the Map or Reduce
tasks are written in R, or if those components are written in other
languages and only the resulting output histograms need to be
manipulated in R.

\section{Application: Sending/receiving Interaction With Servers}

Unlike Apache Thrift, Protocol Buffers do not include a concrete RPC
implementation.  However, serialized protocol buffers can trivially be
sent over TCP or integrated with a proprietary RPC system.  Combined
with an RPC system this means that one can interactively craft request
messages, send the serialized message to a remote server, read back a
response, and then parse the response protocol buffer interactively.

TODO(mstokely): Talk about Jeroen Ooms OpenCPU, or talk about Andy
Chu's Poly.

>>>>

\include{app-mapreduce}

%\section{Application: Sending/receiving Interaction With Servers}
%
%Combined
%with an RPC system this means that one can interactively craft request
%messages, send the serialized message to a remote server, read back a
%response, and then parse the response protocol buffer interactively.

%TODO(mstokely): Talk about Jeroen Ooms OpenCPU, or talk about Andy
%Chu's Poly.
